Viscous Transport in Eroding Porous Media

### 2019-05-15 docs/transport/erosion_transport.tex
Added Shelley refrence
do the result section in transport paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Contributions}
\begin{itemize}
  \item Use novel near-singular Barycentric integration scheme for
    Stokes equation outlined in~\cite{bar-wu-vee2015}.
  \item Need to compute one additional derivative since we need the
    derivative of the velocity to find the vorticity and stress tensor
  \item Annealing algorithm to create initial body configurations of specified area fraction specified size distribution (NM can do the writing for this).
  \item Tracer trajectories at different time steps
  \item Compute the anomalous diffusion rate using similar techniques as
    the paper with Pietro~\cite{dea-qua-bir-jua2018}
  \item Need a novel way to do time stepping through the complex
    geometry
\end{itemize}

@@

Besides the channels between two bodies, there is a single channel

@@

Since the direction of flow is from left to right, most of the tracers will not travel vertically but horizontally when the gaps or channels are too small.  }

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Contributions}
\begin{itemize}
  \item Use novel near-singular Barycentric integration scheme for
    Stokes equation outlined in~\cite{bar-wu-vee2015}. (Remember to include historically significant reference Shelley \cite{baker1986boundary}).
  \item Need to compute one additional derivative since we need the
    derivative of the velocity to find the vorticity and stress tensor
  \item Annealing algorithm to create initial body configurations of specified area fraction specified size distribution (NM can do the writing for this).
  \item Tracer trajectories at different time steps
  \item Compute the anomalous diffusion rate using similar techniques as
    the paper with Pietro~\cite{dea-qua-bir-jua2018}
  \item Need a novel way to do time stepping through the complex
    geometry
\end{itemize}

@@

Besides the channels between two bodies, there is a single channel 
goes across the domain horizontally and
 the flow has been concentrated in this channel. 
In the second frame of Fig.~\ref{fig:Eroding20vort},
 this channel is between bodies 1 \& 20, 1 \& 9, 4 \& 3, 8 \& 11, 8 \& 2, 6 \& 12, and 6 \& 19. 
We can get a better understanding of this channel from 
the trajectories of tracers in Fig.~\ref{fig:Eroding20tracer}. 
In the top three frames of  Fig.~\ref{fig:Eroding20tracer},
the flow (or tracer) first comes from three small channels 
between outer boundary \& body 10, bodies 7 \& 14, and bodies 14 \& 18, 
then the three branches become one and go into the main channel between bodies 1 \& 9. 
From the first frame to the forth frame of Fig.~\ref{fig:Eroding20vort}, 
this channel is expanding faster than other channel 
and bodies 4 \& 12 has vanished and body 19 is almost gone in the forth frame. 
The reason of fast expansion of this channel is the high vorticity. 
In the forth frame of Fig.~\ref{fig:Eroding20tracer}, 
we could see the vorticity is relatively high on the side of bodies which form this channel
so the bodies are eroded fast on the side of this channel or have vanished completely.

Furthermore, how long the body lasts for depends on not only the size of the body 
but also the location of the body. 
For example, the first three vanishing bodies are 
body 12 (as t=0.0256), 4 (as t=0.0278), then 17 (as t=0.0287). 
Since body 4 is located in the main flow channel so 
the body 4 is vanished earlier than body 17 
even the initial size of body 4 is larger than the size of body 17.
This channel will keep expanding and the bodies around this channel will vanish earlier than others. 
After body 17, the next 8 vanishing bodies with respect to time are body 19 (as t=0.0312),  
 body 7 (as t=0.0325), body 20 (as t=0.0329), body 8 (as t=0.0349), body 10 (as t=0.0353),
 body 3 (as t=0.0356), body 14 (as t=0.0363), then body 9 (as t=0.0376).  
All of these eight bodies are around this channel.

@@

Although the direction of flow is from left to right, 
the tracers will not only travel horizontally but vertically. 
In the last three frames of Fig.~\ref{fig:Eroding20tracer},  }
